Type Refinements for the Working Class

### 2015-12-20 paper.tex
correct outdated notation
Explain why we're defining refinements for arbitrary rho : Y -> Y'

We have the bottom refinement $\GloballyRefines{\TyBot{\tau}}{\tau}$, which
simply contains no elements. Next, the top refinement
$\GloballyRefines{\TyTop{\tau}}{\tau}$ identifies all terms
$\Member{M,N}{\Exprs_\tau(\Upsilon)}$.  The join (union)
$\Refines{\Upsilon}{\phi\cup\psi}{\tau}$ of two refinements
$\Refines{\Upsilon}{\phi}{\tau}$ and $\Refines{\Upsilon}{\psi}{\tau}$ is defined as
follows:

\begin{gather*}
  \infer{
    \RMemEq{\Upsilon}{M}{N}{\phi\cup\psi}
  }{
    \RMemEq{\Upsilon}{M}{N}{\phi}
  }\qquad
  \infer{
    \RMemEq{\Upsilon}{M}{N}{\phi\cup\psi}
  }{
    \RMemEq{\Upsilon}{M}{N}{\psi}
  }
\end{gather*}

Finally the meet (intersection) $\Refines{\Upsilon}{\phi\cap\psi}{\tau}$ of two refinements
$\Refines{\Upsilon}{\phi}{\tau}$ and $\Refines{\Upsilon}{\psi}{\tau}$ is defined
dually:
\[
  \infer{
    \RMemEq{\Upsilon}{M}{N}{\phi\cap\psi}
  }{
    \RMemEq{\Upsilon}{M}{N}{\phi} &
    \RMemEq{\Upsilon}{M}{N}{\psi}
  }
\]

@@

@@

For a lazy computation language
$\Match{L}{\Tuple{\Sorts,\Operators,\CanOperators}}$, let us define
sort-indexed (resp.\ valence-indexed) copresheaves on $\SCtx$ of closed values
(resp\. bound terms) as follows:
\begin{align*}
  \ADefine{\Values_\tau(\Upsilon)}{
    \MkSet{
      M\equiv\App{\vartheta}{\vec{E}}
      \mid M\in\Exprs_\tau(\Upsilon)\land \exists a. \CanOperators\Pair{\Upsilon}{a}\ni\vartheta
    }
  }\\
  \ADefine{
    \BTms_{v}(\Upsilon)
  }{
    \MkSet{E \mid \IsAbtUnmoded{\cdot}{\Upsilon}{\cdot}{E}{v}}
  }
\end{align*}

>>>>

We have the bottom refinement $\GloballyRefines{\TyBot{\tau}}{\tau}$, which
simply contains no elements. Next, the top refinement
$\GloballyRefines{\TyTop{\tau}}{\tau}$ identifies all terms
$\Member{M,N}{\Exprs_\tau(\Upsilon)}$.  The join (union)
$\Refines{\Upsilon}{\phi\cup\psi}{\tau}$ of two refinements
$\Refines{\Upsilon}{\phi}{\tau}$ and $\Refines{\Upsilon}{\psi}{\tau}$ is defined as
follows, for any
\begin{tikzcd}[cramped, ampersand replacement = \&]
  \IMode{\Upsilon} \arrow[r,hook,"\IMode{\rho}"] \&\IMode{\Upsilon'}
\end{tikzcd}:

\begin{gather*}
  \infer{
    \RMemEq{\Upsilon'}{M}{N}{\phi\cup\psi}
  }{
    \RMemEq{\Upsilon'}{M}{N}{\phi}
  }\qquad
  \infer{
    \RMemEq{\Upsilon'}{M}{N}{\phi\cup\psi}
  }{
    \RMemEq{\Upsilon'}{M}{N}{\psi}
  }
\end{gather*}

Finally the meet (intersection) $\Refines{\Upsilon}{\phi\cap\psi}{\tau}$ of two refinements
$\Refines{\Upsilon}{\phi}{\tau}$ and $\Refines{\Upsilon}{\psi}{\tau}$ is defined
dually:
\[
  \infer{
    \RMemEq{\Upsilon'}{M}{N}{\phi\cap\psi}
  }{
    \RMemEq{\Upsilon'}{M}{N}{\phi} &
    \RMemEq{\Upsilon'}{M}{N}{\psi}
  }
\]

@@

\begin{remark}
  Observe that \emph{definition} of a refinement
  $\Refines{\Upsilon}{\phi}{\tau}$ is given in terms of an arbitrary
  $\Upsilon'$ that is related to $\Upsilon$ by a renaming. This is because
  $\Upsilon$ is the stage at which the refinement has come into being, but the
  definition of the refinement must be applicable at all subsequent stages.
\end{remark}

@@

For a lazy computation language
$\Match{L}{\Tuple{\Sorts,\Operators,\CanOperators}}$, let us define
sort-indexed (resp.\ valence-indexed) copresheaves on $\SCtx$ of closed values
(resp\. bound terms) as follows:
\begin{align*}
  \ADefine{\Values_\tau(\Upsilon)}{
    \MkSet{
      M\equiv\App{\vartheta}{\vec{E}}
      \mid M\in\Exprs_\tau(\Upsilon)\land \exists a. \CanOperators_a(\Upsilon)\ni\vartheta
    }
  }\\
  \ADefine{
    \BTms_{v}(\Upsilon)
  }{
    \MkSet{E \mid \IsAbtUnmoded{\cdot}{\Upsilon}{\cdot}{E}{v}}
  }
\end{align*}
